PANCHANGE_data_preprocessing

### 2020-08-19 PANCHANGE_data_preprocessing2020-07-15.Rmd
added ocir availability chunk

>>>>

OCI-R
```{r glad/edgi data level groups ocir}
if(GLAD == TRUE | EDGI == TRUE){
dat <- dat %>%
  mutate(
    data_group_ocir_numeric =
      case_when(
        na_per_person_ocir_base == 0 & na_per_person_ocir_prepan == 0 & na_per_person_ocir_retro == 0 ~ 5, #all complete baseline, prepan and retro
        na_per_person_ocir_base != 0 & na_per_person_ocir_prepan != 0 & na_per_person_ocir_retro == 0  ~ 4, #retro data only
        na_per_person_ocir_base == 0 & na_per_person_ocir_prepan != 0 & na_per_person_ocir_retro != 0  ~ 3, #baseline data only
        na_per_person_ocir_base == 0 & na_per_person_ocir_prepan == 0 & na_per_person_ocir_retro != 0  ~ 2, #prepan and baseline data only
        na_per_person_ocir_base == 0 & na_per_person_ocir_prepan != 0 & na_per_person_ocir_retro == 0 ~ 1,  #baseline and retro data only
        na_per_person_ocir_base != 0 & na_per_person_ocir_prepan == 0 & na_per_person_ocir_retro != 0  ~ 0  #prepan data only
      )
  )

dat <- dat %>%
  mutate(
    data_group_ocir = 
      recode_factor(
        data_group_ocir_numeric,
        "0" = "Only prepandemic data",
        "1" = "Baseline and retrospective data",
        "2" = "Prepandemic and baseline data",
        "3" = "Baseline data only",
        "4" = "Retrospective data only",
        "5" = "All prepandemic, baseline and retrospective data"
      )
  )

table(dat$data_group_ocir)
}
```

```{r nbr/ramp data level groups ocir}
if(NBR == TRUE | RAMP == TRUE){
dat <- dat %>%
  mutate(
    data_group_ocir_numeric =
      case_when(
#        na_per_person_ocir_base == 0 & na_per_person_ocir_prepan == 0 & na_per_person_ocir_retro == 0 ~ 5, #all complete baseline, prepan and retro
        na_per_person_ocir_base != 0 & na_per_person_ocir_retro == 0  ~ 4, #retro data only
        na_per_person_ocir_base == 0 & na_per_person_ocir_retro != 0  ~ 3, #baseline data only
#        na_per_person_ocir_base == 0 & na_per_person_ocir_prepan == 0 & na_per_person_ocir_retro != 0  ~ 2, #prepan and baseline data only
        na_per_person_ocir_base == 0 & na_per_person_ocir_retro == 0 ~ 1  #baseline and retro data only
#        na_per_person_ocir_base != 0 & na_per_person_ocir_prepan == 0 & na_per_person_ocir_retro != 0  ~ 0  #prepan data only
      )
  )

dat <- dat %>%
  mutate(
    data_group_ocir = 
      recode_factor(
        data_group_ocir_numeric,
        "0" = "Only prepandemic data",
        "1" = "Baseline and retrospective data",
        "2" = "Prepandemic and baseline data",
        "3" = "Baseline data only",
        "4" = "Retrospective data only",
        "5" = "All prepandemic, baseline and retrospective data"
      )
  )

table(dat$data_group_ocir)
}
```
